Chapter 2 Figures

### 2019-12-30 doc/figureFiles/figures.Rmd
outlining for final figure

@@

First run of the vertica facets looks awful and squished. fix it.

>>>>

# FINAL DRAFT

put together 3 pieces; plot, cell1, cell2

 todo

   1. finish and import final ai edited polt,

   2. add cell images with cowplot to bottom

```{r load.plot, echo=FALSE}

```{r load.cells, echo=FALSE}

cell.output <- readPNG('C:/Users/alpeterson7/Documents/WildMiceMadison/Images/whole_cell_example.png')
#make empty DF for ggplot object
empty.DF <- data.frame(col1 = c(1,3), col2 = c(1,3) )
#make an empty ggplot thing, then background ontop
spermatocyte.auto <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(cell.output) + theme(axis.title.x=element_blank(),
                                  axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

```{r cow.plot, echo=FALSE}

library("cowplot")
fig1  <- ggdraw() +
  draw_plot(MLH1.fig1, x = 0, y = .42, width=1, height=.55) +

  draw_plot(Better_MAD_map, x=0, y=0, width=.4, height=.4) +

  draw_plot(spermatocyte, x=.38, y = 0, width=.31, height=.39) +

  draw_plot(spermatocyte.auto, x=.69, y = 0, width = .31, height = .39) +

  draw_plot_label(label = c("A", "B", "C"), size = 15,
                  x = c(0, 0, .36), y = c(1, .43, 0.43) )

fig1

ggsave("~./WildMiceMadison/results/Figure1_32119.png")
```

@@
